A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum sequential games with imcomplete information

### 2015-07-23 paper.tex
major changes

\maketitle
\begin{abstract}We present a simple primal-dual algorithm for
  computing approximate Nash equilibria in two-person zero-sum
  sequential games with  imcomplete information and perfect recall
  (like Texas Hold'em Poker) based on the notion of enlarged
  subgradients. Our algorithm only performs basic iterations (i.e
  iterations involving no calls to external first-order oracles, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with imcomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  \cite{koller1992complexity} which allows us to encode any such game
  as a matrix game with polyhedral strategy profiles, the size of the
  representation being linear in ... The number of iterations needed
  to produce a Nash equilibrium with a given precision is inversely
  proportional to the desired precision. As proof-of-concept, we apply our
  algorithm to solve Kuhn 3-card Poker.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
A game-theoretic approach to playing games strategically optimally
consists in computing Nash-equilibria (infact, approximations thereof)
offline, and playing one's part of the equilibrium online. This
technique is the driving-force behind solution concepts like CFR
\cite{zinkevich2008regret,lanctot2009monte},
$\text{CFR}^{+}$ \textbf{TODO: add ref!!!}, and other variants, which
have recently had profound success in Poker. However, solving games
for equilibria remains a mathematical and computational challenge,
especially in sequential games with imperfect information. This paper
proposes a simple and fast algorithm for solving for such equilibria
approximately, in a sense which will be made clear shortly.

\subsection{Notation, terminology, and some aspects of modern convex analysis}
\paragraph{\textbf{General notions.}}
Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
of all subsets of $X$, or equivalently the set of all binary
functions on $X$. Let $m$ and $n$ be positive integers. Given two
vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
$\langle z, w\rangle := \sum_{j}z_jw_j$. The components of $z$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). The notation ``$z \ge 0$'' means that all the components of
$z$ are nonnegative.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  $\|z\|$ denotes the
$2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{\langle z,
  z\rangle}$. $(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the
point-wise maximum of $z$ with $0$. For example, $((-2, \pi))_+ =
(max(-2, 0), max(\pi, 0)) = (0, \pi)$. The operator $(.)_+$ is the
well-known (multi-dimensional) \textit{ramp} function. The
$n$-simplex denoted $\Delta_n$, is defined by $\Delta_n := \{z \in
\mathbb{R}^n_+|z_0 + z_1 + ... z_{n - 1} = 1\}$.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

\paragraph{\textbf{Modern convex analysis.}}
Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
\begin{eqnarray}
  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by
\begin{eqnarray}
  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z).
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthogonal projectors. For example
$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
(z)_+$. One also has the useful characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

\subsection{Nash-equilibrium concepts and statement of the problem}
\subsubsection{Preliminaries}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
established that for sequential two-person zero-sum games with
imcomplete information and perfect recall, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

\subsubsection{A note about matrix games on simplexes.} It should be
noted
that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
  game with payoff matrix $A$, for which each player's strategy
profile is a simplex; this simplex can be written in the form
\eqref{eq:polyhedron} by taking $E_k := (1, 1, ..., 1) \in
\mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
matrix game on simplexes can be seen as a sequential game.  Thus the
results presented in this manuscript can be trivially applied such
games in particular. Here, the polyhedral strategy profiles $Q_k$
defined in \eqref{eq:polyhedron} reduce to simplexes $\Delta_{n_k}$,
and the primal-dual gap function $G(x,y)$ writes
\begin{eqnarray}G(x, y) =
\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
\Delta_{n_1} \times \Delta_{n_2}\} = \underset{0 \le j <
  n_1}{\text{max }}(Ay)_j - \underset{0 \le i < n_2}{\text{min
}}(A^Tx)_i.
\end{eqnarray}

\subsubsection{Approximate feasibility and optimality}
Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
is impossible in practice (indeed, this system of problems is NP-hard
\cite{koller1992complexity}) and such a precision doesn't have any
fundamental practical advantage. Instead, it is customary compute
``approximate'' Nash equilibria.

@@

Let us now, introduce the notion of $\epsilon$-subgradients
\cite{he2013accelerating}.

\begin{definition}[$\epsilon$-subgradient]
Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ is the set-valued function
\begin{eqnarray}
\partial_\epsilon f: \mathbb{R}^n \rightarrow
2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
\mathbb{R}^n\}.
\end{eqnarray}
\end{definition}

The idea behind $\epsilon$-subgradients is the following. Say we wish
to minimize the function $f$. Replace the usual necessary
condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
small vector $v$''. In fact, it is easy to see that, for each
point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
This approximation concept for subgradients yields the following
concept of approximate Nash equlibria (adapted from
\cite{he2013accelerating}).

\subsection{Our contribution}
We develop a $\mathcal{O}(1/\epsilon)$ primal-dual
algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\epsilon,
  0)$-equilibria in sequential two-person zero-sum games with
  imcomplete information and perfect recall.

@@

@@

\subsection{Practical considerations}
\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo} most of the time is spent
pre-multiplying vectors by $A$ and $A^T$. For \textit{flop}-type Poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}.

@@

\section{Experimantal results}
\label{sec:results}
To access the practical quality of the proposed algorithm, we
experimented it on real and simulated matrix games.

\begin{figure}[!htpb]
  \subfigure[Matrix game on simplices]{
    \includegraphics[width=.33\linewidth]{simplex_dgap.pdf}
  }
  \hspace{-2em}
  \subfigure[Toy Poker]{
    \includegraphics[width=.33\linewidth]{SimplifiedPoker_dgap.pdf}
  }
  \hspace{-2em}
  \subfigure[Kuhn 3-card Poker]{
    \includegraphics[width=.33\linewidth]{Kuhn3112_dgap.pdf}
  }
  \vspace{-1em}
  \hspace{-1em}
  \includegraphics[width=.34\linewidth]{simplex_NE.pdf}
  \hspace{-1em}
  \includegraphics[width=.33\linewidth]{SimplifiedPoker_NE.pdf}
  \hspace{-1em}
  \includegraphics[width=.33\linewidth]{Kuhn3112_NE.pdf}
  \caption{Convergence curves of Algorithm
    \ref{Tab:algo}. \textbf{Top row}: Evolution of ergodic
    primal-dual gap. \textbf{Bottom row}: Evolution of
    value of game.}
  \label{Tab:dgap_curve}
\end{figure}

\paragraph{\textbf{Matrix game on simplexes.}}
As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
\times 1000$ random matrix whose entries are uniformly identically
distributed in the closed interval $[-1, 1]$.

\paragraph{\textbf{Toy Poker game.}}
The sequence-form representation for this Toy Poker game is given by
(showing only nonzero entries):\\

$E_1 \in \mathbb{R}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
E_1(1,2) = E_1(2,3) = E_1(2,4) = {1}$,
$E_1(1,0) = E_1(2,0) = {-1}$; \\

$E_2 \in \mathbb{R}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
= E_2(2,3) = E_2(2,4) = {1}$, $E_2(1,0) = E_2(2,0) =
{-1}$; and \\

$A \in \mathbb{R}^{5 \times 5}$ with $A(2,0) =
A(4,0) = {-0.5}$, $A(1,3) = {1}$, $A(3,1) =
{-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = {0.25}$.

\paragraph{{Kuhn 3-card Poker.}}
The game has $n_1 = n_2 = 13$ and $l_1 = l_2 = 7$, and its
sequence-form is given by:\\

$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
E_1(5,5) = E_1(6,9) = {-1}$; \\

 $E_2 \in \mathbb{R}^{7 \times 13}$ with
$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
E_2(5,0) = E_2(6,0) = {-1}$; and \\

 $A \in \mathbb{R}^{13 \times
  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
A(12,1) = A(12,5) = {0.166667}$.\\

>>>>

\maketitle
\begin{abstract}We present a simple primal-dual algorithm for
  computing approximate Nash equilibria in two-person zero-sum
  sequential games with  imcomplete information and perfect recall
  (like Texas Hold'em Poker). Our algorithm only performs basic
  iterations (i.e iterations involving no calls to external
  first-order oracles, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with imcomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  \cite{koller1992complexity} which allows us to encode any such game
  as a matrix game with polyhedral strategy profiles. We prove that
  the number of iterations needed to produce a Nash equilibrium with a
  given precision is inversely proportional to the desired
  precision. We also present experimental results on simulated and
  real games (Kuhn poker).
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
A game-theoretic approach to playing games strategically optimally
consists in computing Nash-equilibria (infact, approximations thereof)
offline, and playing one's part (an optimal \textit{behavioral}
strategy) of the equilibrium online. This
technique is the driving-force behind solution concepts like CFR
\cite{zinkevich2008regret,lanctot2009monte},
$\text{CFR}^{+}$ \cite{tammelin14} and other variants, etc., which
have recently had profound success in Poker. However, solving games
for equilibria remains a mathematical and computational challenge,
especially in sequential games with imperfect information. This paper
proposes a simple and fast algorithm for solving for such equilibria
approximately, in a sense which will be made clear shortly.

\subsection{Notation and terminology}
Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
of all subsets of $X$, or equivalently the set of all binary
functions on $X$. Let $m$ and $n$ be positive integers. Given two
vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
$\langle z, w\rangle := \sum_{j}z_jw_j$. The components of $z$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). The notation ``$z \ge 0$'' means that all the components of
$z$ are nonnegative.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  $\|z\|$ denotes the
$2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{\langle z,
  z\rangle}$. $(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the
point-wise maximum of $z$ with $0$. For example, $((-2, \pi))_+ =
(max(-2, 0), max(\pi, 0)) = (0, \pi)$. The operator $(.)_+$ is the
well-known (multi-dimensional) \textit{ramp} function. The
$n$-simplex denoted $\Delta_n$, is defined by $\Delta_n := \{z \in
\mathbb{R}^n_+|\sum_j z_j = 1\}$.
Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

\subsection{Nash-equilibrium concepts and statement of the problem}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
established that for sequential two-person zero-sum games with
imcomplete information and perfect recall, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
is impossible in practice (indeed, this system of problems is NP-hard
\cite{koller1992complexity}) and such a precision doesn't have any
fundamental practical advantage. Instead, it is customary compute
``approximate'' Nash equilibria. A popular notion of approximate
equilibria is the following:

@@

\paragraph{Our contribution.}
Developing on an alternative notion of approximate equilibria
homologuous to that presented in Definition \ref{thm:approx_nash}, we
device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
computing approximate Nash equilibria in sequential two-person
zero-sum games with imcomplete information and perfect recall. We also
prove that the number of iterations required by the algorithm to
produce an approximation equilibrium to a precision $\epsilon$ is
$\mathcal{O}(1/\epsilon)$.

\paragraph{A note about matrix games on simplexes.} It should be
noted
that any matrix $A \in \mathbb{R}^{n_1 \times n_2}$ specifies a matrix
  game with payoff matrix $A$, for which each player's strategy
profile is a simplex; this simplex can be written in the form
\eqref{eq:polyhedron} by taking $E_k := (1, 1, ..., 1) \in
\mathbb{R}^{1 \times n_k}$ and $e_k = 1 \in \mathbb{R}^1$. Thus every
matrix game on simplexes can be seen as a sequential game.  Thus the
results presented in this manuscript can be trivially applied such
games in particular. Here, the polyhedral strategy profiles $Q_k$
defined in \eqref{eq:polyhedron} reduce to simplexes $\Delta_{n_k}$,
and the primal-dual gap function $G(x,y)$ writes
\begin{eqnarray}G(x, y) =
\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle | (u,v) \in
\Delta_{n_1} \times \Delta_{n_2}\} = \underset{0 \le j <
  n_1}{\text{max }}(Ay)_j - \underset{0 \le i < n_2}{\text{min
}}(A^Tx)_i.
\end{eqnarray}

@@

\section{A more amenable notion of approximate equilibrium}
\subsection{Interlude: Proximal calculus}
Let us introduce some notions in modern convex analysis which will be
useful in what follows. Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
\begin{eqnarray}
  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by
\begin{eqnarray}
  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z).
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthogonal projectors. For example
$\prox_{i_{\mathbb{R}^n_+}}(z) \equiv \proj_{\mathbb{R}^n_+}(z) \equiv
(z)_+$. One also has the useful characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ is the set-valued function
\begin{eqnarray}
\partial_\epsilon f: \mathbb{R}^n \rightarrow
2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
\mathbb{R}^n\}.
\end{eqnarray}

The idea behind $\epsilon$-subgradients is the following. Say we wish
to minimize the function $f$. Replace the usual necessary
condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
small vector $v$''. In fact, it is easy to see that, for each
point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.

This approximation concept for subgradients yields the following
concept of approximate Nash equlibria (adapted from
\cite{he2013accelerating}).

@@

\subsection{Practical considerations}
\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo} most of the time is spent
pre-multiplying vectors by $A$ and $A^T$. For \textit{flop-type} poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{100}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}.

@@

\section{Experimental results}
\label{sec:results}
To access the practical quality of the proposed algorithm, we
experimented it on real games.

\subsection{Basic test-bed: Matrix games on simplexes}
As in \cite{nesterov2005a,chambolle2014ergodic}, we generate a $1000
\times 1000$ random matrix whose entries are uniformly identically
distributed in the closed interval $[-1, 1]$.

\begin{figure}[!htpb]
  \subfigure[Matrix game on simplexes]{
    \includegraphics[width=.33\linewidth]{0.pdf}
  }
  \hspace{-2em}
  \subfigure[Toy Poker]{
    \includegraphics[width=.33\linewidth]{SimplifiedPoker_dgap.pdf}
  }
  \hspace{-2em}
  \subfigure[Kuhn 3-card Poker]{
    \includegraphics[width=.33\linewidth]{Kuhn3112_dgap.pdf}
  }
  \vspace{-1em}
  \hspace{-1em}
  \includegraphics[width=.34\linewidth]{1.pdf}
  \hspace{-1em}
  \includegraphics[width=.33\linewidth]{SimplifiedPoker_NE.pdf}
  \hspace{-1em}
  \includegraphics[width=.33\linewidth]{Kuhn3112_NE.pdf}
  \caption{Convergence curves of Algorithm
    \ref{Tab:algo}. \textbf{Top row}: Evolution of ergodic
    primal-dual gap. \textbf{Bottom row}: Evolution of
    value of game.}
  \label{Tab:dgap_curve}
\end{figure}

\subsection{Sequential games with imcomplete information}
\paragraph{\textbf{Toy Poker game...}}
%% The sequence-form representation for this Toy Poker game is given by
%% (showing only nonzero entries):\\

%% $E_1 \in \mathbb{R}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
%% E_1(1,2) = E_1(2,3) = E_1(2,4) = {1}$,
%% $E_1(1,0) = E_1(2,0) = {-1}$; \\

%% $E_2 \in \mathbb{R}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
%% = E_2(2,3) = E_2(2,4) = {1}$, $E_2(1,0) = E_2(2,0) =
%% {-1}$; and \\

%% $A \in \mathbb{R}^{5 \times 5}$ with $A(2,0) =
%% A(4,0) = {-0.5}$, $A(1,3) = {1}$, $A(3,1) =
%% {-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = {0.25}$.

\paragraph{{Kuhn 3-card Poker}} is a simplified form of poker
developed by Harold W. Kuhn. It is a zero sum two player game. The
deck includes only three playing cards, for example a King, Queen, and
Jack. One card is dealt to each player, then the first player must bet
or pass, then the second player may bet or pass. If any player chooses
to bet the opposing player must bet as well ("call") in order to stay
in the round. After both players pass or bet the player with the
highest card wins the pot. Kuhn demonstrated that there are many game
theoretic optimal strategies for the first player in this game, but
only one for the second player, and that, when played optimally, the
first player should expect to lose at a rate of −1/18 per hand. The
sequence-form representation of the game has $n_1 = n_2 = 13$
sequences and $l_1 = l_2 = 7$ information
sets per player. More details (payoff matrix, etc.) are provided in
the supp. mats. %% , and its
%% sequence-form is given by:\\

%% $E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
%% E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
%% E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
%% E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
%% E_1(5,5) = E_1(6,9) = {-1}$; \\

%%  $E_2 \in \mathbb{R}^{7 \times 13}$ with
%% $E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
%% E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
%% E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
%% E_2(5,0) = E_2(6,0) = {-1}$; and \\

%%  $A \in \mathbb{R}^{13 \times
%%   13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
%% {-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
%% A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
%% A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
%% $A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
%% A(12,1) = A(12,5) = {0.166667}$.\\
